Next Trippy Structures\thanks{Supported by organization x.}

### 2019-01-31 paper.tex
Explained CiNCT

\subsubsection{Network constrained trajectory indexing}
There are also numerous approaches that use R-Tree based indexes for trajectories that are constrained to an underlying network, aiming to decrease the redundancy in the representation by separating the representation into levels. Examples of such indexes include the {\em FNR-Tree}~\cite{DBLP:conf/ssd/Frentzos03}, where the network elements are indexed with a 2D R-Tree and 1D R-Trees to index time intervals of moving objects along the edges of the network. Some of the limitations of the FNR-Tree are addressed in \cite{DBLP:journals/geoinformatica/AlmeidaG05}, where the authors propose the {\em MON-Tree}, where the moving objects are indexes in two dimensional R-Trees (the dimensions being edge position vs time). More recent alternatives also integrate {\em B$⁺$-Trees}, which has proven to be more space and time efficient for indexing the temporal dimension as proven by the {\em TMN-Tree}~\cite{chang2010tmn}. Refer to \cite{john2017performance} for a quick comparison of these R-Tree based indexes.

As a competitive alternative to these R-Tree based indexes, {\em PARINET}~\cite{DBLP:journals/vldb/PopaZOBV11}, that builds spatial partitions from the trajectories based on their distribution and network topology, and uses a B$⁺$-Tree to index the trajectories in each partition by time intervals. Although candidate trajectories must be filtered in memory during queries, PARINET is highly efficient in practice as it minimizes the number of disk accesses needed.
%The same ideas were used in {\em TRIFL}~\cite{that2015trifl}, where the cost model is adapted for flash storage.

@@

Apart from \cite{koide2018cinct}, in compact data structures there \cite{rivera2018faster}, which introduces two bitvectors to efficiently answer time interval queries and us...

>>>>

\subsubsection{Network constrained trajectory indexing}
There are also numerous approaches that use R-Tree based indexes for trajectories that are constrained to an underlying network, aiming to decrease the redundancy in the representation by separating the representation into levels. Examples of such indexes include the {\em FNR-Tree}~\cite{DBLP:conf/ssd/Frentzos03}, where the network elements are indexed with a 2D R-Tree and 1D R-Trees to index time intervals of moving objects along the edges of the network. Some of the limitations of the FNR-Tree are addressed in \cite{DBLP:journals/geoinformatica/AlmeidaG05}, where the authors propose the {\em MON-Tree}, where the moving objects are indexes in two dimensional R-Trees (the dimensions being edge position vs time). More recent alternatives also integrate {\em B$^+$-Trees}, which has proven to be more space and time efficient for indexing the temporal dimension as proven by the {\em TMN-Tree}~\cite{chang2010tmn}. Refer to \cite{john2017performance} for a quick comparison of these R-Tree based indexes.

As a competitive alternative to these R-Tree based indexes, {\em PARINET}~\cite{DBLP:journals/vldb/PopaZOBV11}, that builds spatial partitions from the trajectories based on their distribution and network topology, and uses a B$^+$-Tree to index the trajectories in each partition by time intervals. Although candidate trajectories must be filtered in memory during queries, PARINET is highly efficient in practice as it minimizes the number of disk accesses needed.
%The same ideas were used in {\em TRIFL}~\cite{that2015trifl}, where the cost model is adapted for flash storage.

@@

\marginpar{We should probably cite our previous work too, right?}
A recent compact data structure names {\em CiNCT} has been proposed in \cite{koide2018cinct}, where trajectories are encoded into a string, that is used to build an FM-index \cite{DBLP:conf/focs/FerraginaM00} with a Huffman-shaped Wavelet Tree \cite{ferragina2009compressed}. To further save space, the string is constructed with relative movement labels instead of absolute edges, with an auxiliary structure that represents a network graph built from the input trajectories themselves. While this structure excels at pattern-matching and path extraction in vehicular networks (such as the streets of a city), it cannot be applied to our problems in public transportation networks.

\marginpar{\cite{rivera2018faster} is just 2 bitmaps to answer queries on time intervals, not directly related to trajectories despite what the title suggests. Should we cite it just to be nice? If so, then how?}
% \cite{rivera2018faster}, which introduces two bitvectors to efficiently answer time interval queries and us...
